Figures

### 2019-01-15 manuscript/figures.Rmd
mention p values in fig 4 caption

```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.cap="Correlation among connectivity metrics and selected lake characteristics. WS is the lake watershed extent whereas SWS is the lake subwatershed extent. Connectivity metrics are defined in Figure 2.", message=FALSE}
knitr::include_graphics("../figures/07_cor_mat_hmap-1.pdf")
```

>>>>

```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.cap="Correlation among connectivity metrics and selected lake characteristics. Cell shading and color reflects the correlation coefficient value. Only coefficients accompanied by a significant p value < 0.05 are shown as text. Here, WS is the lake watershed extent whereas SWS is the lake subwatershed extent. Connectivity metrics are defined in Figure 2.", message=FALSE}
knitr::include_graphics("../figures/07_cor_mat_hmap-1.pdf")
```
